Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-08 project.after.Rmd
renaming variables

```{r seasonalities/before}
aggregated.final <- seasonality.aggregate(final.training)
season.final.24 <- trend_season(aggregated.final, 24)
season.final.168 <- trend_season(aggregated.final-season.final.24$seasonal, 168)

season.final.24 <- trend_season(aggregated.final-season.final.168$seasonal, 24)
season.final.168 <- trend_season(aggregated.final-season.final.24$seasonal, 168)

# this third iteration isn't actually needed
season.final.24 <- trend_season(aggregated.final-season.final.168$seasonal, 24)
season.final.168 <- trend_season(aggregated.final-season.final.24$seasonal, 168)

residuals.final <- aggregated.final-season.final.24$seasonal-season.final.168$seasonal-season.final.168$trend

seasonbase.final.24 <- trend_season(aggregated.final, 24)
seasonbase.final.168 <- trend_season(aggregated.final, 168)

plot_grid(
  autoplot(ts(seasonbase.final.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.final.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.final.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.final.168$figure + rep(season.final.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.final.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.final.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.final.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

```{r seasonalities/lockdown}
aggregated.lockdown <- seasonality.aggregate(final.testing)
season.lockdown.24 <- trend_season(aggregated.lockdown, 24)
season.lockdown.168 <- trend_season(aggregated.lockdown-season.lockdown.24$seasonal, 168)

season.lockdown.24 <- trend_season(aggregated.lockdown-season.lockdown.168$seasonal, 24)
season.lockdown.168 <- trend_season(aggregated.lockdown-season.lockdown.24$seasonal, 168)

# this third iteration isn't actually needed
season.lockdown.24 <- trend_season(aggregated.lockdown-season.lockdown.168$seasonal, 24)
season.lockdown.168 <- trend_season(aggregated.lockdown-season.lockdown.24$seasonal, 168)

residuals.lockdown <- aggregated.lockdown-season.lockdown.24$seasonal-season.lockdown.168$seasonal-season.lockdown.168$trend

seasonbase.lockdown.24 <- trend_season(aggregated.lockdown, 24)
seasonbase.lockdown.168 <- trend_season(aggregated.lockdown, 168)

plot_grid(
  autoplot(ts(seasonbase.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.lockdown.168$figure + rep(season.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.lockdown.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.lockdown.24$figure - season.lockdown.24$sd, ymax = season.lockdown.24$figure + season.lockdown.24$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Daily lockdown")) +
    geom_ribbon(aes(ymin = season.final.24$figure - season.final.24$sd, ymax = season.final.24$figure + season.final.24$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.final.24$figure, col="Daily before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Daily lockdown", "Daily before")),
  autoplot(ts(season.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.lockdown.168$figure - season.lockdown.168$sd, ymax = season.lockdown.168$figure + season.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Weekly lockdown")) +
    geom_ribbon(aes(ymin = season.final.168$figure - season.final.168$sd, ymax = season.final.168$figure + season.final.168$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.final.168$figure, col="Weekly before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before")),
nrow = 2)

autoplot(ts(seasonbase.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = seasonbase.lockdown.168$figure - seasonbase.lockdown.168$sd, ymax = seasonbase.lockdown.168$figure + seasonbase.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="Weekly lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.final.168$figure - seasonbase.final.168$sd, ymax = seasonbase.final.168$figure + seasonbase.final.168$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.final.168$figure, col="Weekly before")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before"))
```

>>>>

```{r seasonalities/before}
aggregated.before.lockdown <- seasonality.aggregate(before.lockdown)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
# this third iteration isn't actually needed
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
seasonbase.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
seasonbase.before.lockdown.168 <- trend_season(aggregated.before.lockdown, 168)

plot_grid(
  autoplot(ts(seasonbase.before.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.before.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.168$figure + rep(season.before.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.before.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.before.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

```{r seasonalities/lockdown}
aggregated.after.lockdown <- seasonality.aggregate(after.lockdown)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
seasonbase.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
seasonbase.after.lockdown.168 <- trend_season(aggregated.after.lockdown, 168)

plot_grid(
  autoplot(ts(seasonbase.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.168$figure + rep(season.after.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.after.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.after.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.after.lockdown.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.24$figure - season.after.lockdown.24$sd, ymax = season.after.lockdown.24$figure + season.after.lockdown.24$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Daily lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.24$figure - season.before.lockdown.24$sd, ymax = season.before.lockdown.24$figure + season.before.lockdown.24$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Daily before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Daily lockdown", "Daily before")),
  autoplot(ts(season.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.168$figure - season.after.lockdown.168$sd, ymax = season.after.lockdown.168$figure + season.after.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Weekly lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.168$figure - season.before.lockdown.168$sd, ymax = season.before.lockdown.168$figure + season.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Weekly before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before")),
nrow = 2)

autoplot(ts(seasonbase.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = seasonbase.after.lockdown.168$figure - seasonbase.after.lockdown.168$sd, ymax = seasonbase.after.lockdown.168$figure + seasonbase.after.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="Weekly lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168$figure - seasonbase.before.lockdown.168$sd, ymax = seasonbase.before.lockdown.168$figure + seasonbase.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168$figure, col="Weekly before")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before"))
```
